---
title: "Multiple Regression Analysis"
author: "Jie Sun"
date: "October 14, 2016"
output: pdf_document
---

## Abstract

In this report we reproduce the analysis from Section 3.2 *Multiple Linear Regression* (chapter 3) of the book **An Introduction to Statistical Learning**.

## Introduction

Given the `Advertising` data, the overall goal is to provide advice on how to improve sales of the particular product. More specifically, the idea is to determine whether there is an association between advertising and sales, and if so, develop an accurate model that can be used to predict sales on the basis of the predictor variables `TV`, `Radio` and `Newspaper` on which advertising budget has been spent. 

In previous assignment `stat159-fall2016-hw02`, we came up with a simple linear regression model which predicts a response `Sales` on the basis of a single predictor variable `TV`. However, in practice we often have more than one predictor. A better approach is to extend the simple linear regression model so that it can directly accommodate multiple predictors. So this analysis focuses on fitting a multiple linear regression model to regress `Sales` onto `TV`, `Radio` and `Newspaper`.

## Data

The Advertising data set consists of `Sales` (in thousands of units) of a particular product in 200 different markets, along with advertising budgets (in thousands of dollars) for the product in each of those markets for three different media (`TV`, `Radio` and `Newspaper`).

## Methodology

To extend the simple regression model, we can give each predictor a separate slope coefficient in a single model. In other words, we're fitting the model:

$$Sales = \beta_0 + \beta_1TV + \beta_2radio + \beta_3newspaper + \epsilon$$

To estimate the coefficients $\beta_0...\beta_3$, we fit the model via the least squares criterion.

## Results

Running three separate simple linear regressions, we compute coefficient estimates of simple regression models: `Sales` on `TV`, `Sales` on `Radio`, and `Sales` on `Newspaper` in Table 1-3. 

```{r results='asis', echo=FALSE}
library(xtable)
load("../data/regression.RData")
st_table = xtable(summary(reg_st), caption = "Simple regression of sales on TV")
print(st_table, comment=FALSE)

sr_table = xtable(summary(reg_sr), caption = "Simple regression of sales on radio")
print(sr_table, comment=FALSE)

sn_table = xtable(summary(reg_sn), caption = "Simple regression of sales on newspaper")
print(sn_table, comment=FALSE)
```


Back to multiple regression, Table 4 displays the coefficient estimates of the least squares model.

```{r results='asis', echo=FALSE}
s_table = xtable(s, caption = "Multiple regression of sales on TV, radio and newspaper")
print(s_table, comment=FALSE)
```

Consider the correlation matrix for the three predictor variables and response variable, displayed in Table 5. It shows that multiple regression suggests no relationship between `sales` and `newspaper` while the simple linear regression implies the opposite.

```{r results='asis', echo=FALSE}
load("../data/correlation-matrix.RData")
cor_table = xtable(cor_matrix, caption = "Correlation matrix for TV, radio, newspaper, and sales for the Advertising data")
print(cor_table, comment=FALSE)
```

We also care about other information of the model like $RSE$, $R^2$ and $F$-statistic listed in Table 6.

```{r results='asis', echo=FALSE}
source("../code/functions/regression-functions.R")
names = c("RSE", "R^2", "F-statistic")
values = c(residual_std_error(reg),
           r_squared(reg),
           f_statistic(reg))
df = data.frame(names, values)
colnames(df) = c("Quantity", "Value")
lsm_table = xtable(df, caption = "More information about the least squares model")
print(lsm_table, comment=FALSE)
```

## Conclusions

Now we're done with the regression analysis, we can address some questions related to the fitness and accuracy of this model. 
